Equalizer\\Programming and User Guide

### 2010-08-21 Developer/ProgrammingGuide/paper.tex
Finalize window API for 1.0, related doxygen and code cleanups: - Make GLEWContext const - mark eq and fabric window methods in doxygen
[x] May break build
[x] May break existing applications
[ ] Bugfix
[ ] New Feature
[x] Cleanup
[ ] Optimization
[x] Documentation

Equalizer uses a C++ programming interface. The API is minimally
invasive, so Equalizer imposes only a minimal, natural execution
framework upon the application. It does not provide a scene graph, or
interferes in any other way with the application's rendering code. The
restructuring work enforced by Equalizer is the minimal refactoring
needed to parallelize the application for rendering.

@@

@@

\begin{description}
\item[eq::base] The eq::base namespace provides C++ classes to abstract
  the underlying operating system and implements common helper
  functionality. One example is the \textsf{eq::base::Clock} class
  providing a high-resolution timer. Classes in this namespace are fully
  documented in the API documentation on the Equalizer website, and are
  not subject of this Programming Guide.
\item[eq::net] The Equalizer network layer provides basic functionality
  for network communication, such as \textsf{Connection} and
  \textsf{ConnectionSet}, as well as higher-level functionality such as
  \textsf{Node}, \textsf{Session} and \textsf{Object}. Please refer to
  \sref{sNetwork} for an introduction into the network layer, and to
  \sref{sNetObject} for distributed objects.
\item[eq] The core namespace for the Equalizer client library. The
  classes and their relationship in this namespace closely model the
  configuration file format. The classes in the \textsf{eq} namespace
  are the main subject of this Programming Guide.
\end{description}

\begin{wrapfigure}{r}{.382\textwidth}
  \includegraphics[width=.382\textwidth]{images/namespaces}
  {\caption{\label{fNamespaces}Namespace Layering for eqPly and eqServer}}
\end{wrapfigure}
Examples shipped with Equalizer are implemented in their own namespaces,
e.g., \textsf{eqPly} or \textsf{eVolve}. They rely mostly on subclassing
classes from the \textsf{eq} namespace, with the occasional usage of
functionality from the \textsf{eq::net} and \textsf{eq::base} namespace.

@@

\fig{fNamespaces} shows the namespace layering for \textsf{eqPly} and
\textsf{eqServer}.

@@

Some applications might rely on a shared filesystem to access the data,
for example when out-of-core algorithms are used. Other applications
prefer to load the data only on the application process, and use
distributed objects to synchronize the scene data with the render
clients.

\begin{wrapfigure}{r}{.382\textwidth}
  \includegraphics[width=.382\textwidth]{images/modelDist.pdf}
  {\caption{\label{fModelDist}Scene Data in eqPly}}
\end{wrapfigure}
\textsf{eqPly} uses static distributed objects to distribute the model
loaded by the application. This approach can be easily extended to
versioned objects to support dynamic data modifications.

>>>>

Equalizer uses a C++ programming interface. The API is minimally
invasive. Equalizer imposes only a minimal, natural execution framework upon the
application. It does not provide a scene graph, or interferes in any other way
with the application's rendering code. The restructuring work enforced by
Equalizer is the minimal refactoring needed to parallelize the application for
scalable, distributed rendering.

@@

The API documentation on the website or in the header files provides a
comprehensive documentation on individual methods, types and other elements of
the API. Methods marked with a specific version are part of the official, public
API and have been introduced by this Equalizer version. Reasonable care is taken
to not break API compatibility or change the semantics of these methods within
future Equalizer versions of the same major revision. Any eventual changes to
the public is documented in the release notes.

In addition the the official, public API Equalizer exposeses a number of
unstable methods and, where unavoidable, internal APIs. These are clearly marked
in the API documentation. Unstable methods may be used by the programmer, but
their interface or functionality may change in any future Equalizer version. The
usage of internal methods is discouraged. Undocumented or unversioned methods
should be considered as part of the unstable API.

@@

\begin{description}
\item[eq::base] The eq::base namespace provides C++ classes to abstract
  the underlying operating system and implements common helper
  functionality. One example is the \textsf{eq::base::Clock} class
  providing a high-resolution timer. Classes in this namespace are fully
  documented in the API documentation on the Equalizer website, and are
  not subject of this Programming Guide.
\item[eq::net] The Equalizer network layer provides basic functionality
  for network communication, such as \textsf{Connection} and
  \textsf{ConnectionSet}, as well as higher-level functionality such as
  \textsf{Node}, \textsf{Session} and \textsf{Object}. Please refer to
  \sref{sNetwork} for an introduction into the network layer, and to
  \sref{sNetObject} for distributed objects.
\item[eq::util] The eq::util namespace provides common utility classes, which
  often the usage of OpenGL functions. Most classes in this namespace are used
  by the the Equalizer client library, but are usable independently from
  Equalizer for application development.
\item[eq] The core namespace for the Equalizer client library. The
  classes and their relationship in this namespace closely model the
  configuration file format. The classes in the \textsf{eq} namespace
  are the main subject of this Programming Guide.
\end{description}

\begin{wrapfigure}{r}{.382\textwidth}
  \includegraphics[width=.382\textwidth]{images/namespaces}
  {\caption{\label{fNamespaces}Namespace Layering for eqPly and eqServer}}
  \vspace{-3ex}
\end{wrapfigure}
Examples shipped with Equalizer are implemented in their own namespaces,
e.g., \textsf{eqPly} or \textsf{eVolve}. They rely mostly on subclassing
classes from the \textsf{eq} namespace, with the occasional usage of
functionality from the \textsf{eq::net} and \textsf{eq::base} namespace.

@@

@@

\begin{wrapfigure}{r}{.382\textwidth}
  \includegraphics[width=.382\textwidth]{images/modelDist.pdf}
  {\caption{\label{fModelDist}Scene Data in eqPly}}
\end{wrapfigure}
Some applications might rely on a shared filesystem to access the data,
for example when out-of-core algorithms are used. Other applications
prefer to load the data only on the application process, and use
distributed objects to synchronize the scene data with the render
clients.

\textsf{eqPly} uses static distributed objects to distribute the model
loaded by the application. This approach can be easily extended to
versioned objects to support dynamic data modifications.
